Resource Buying Games

### 2017-04-02 paper.tex
first 'feature complete' text

\theoremstyle{nonumberplain}
\newframedtheorem{defi}{Definition}
\newframedtheorem{theo}{Theorem}

@@

>>>>

\theoremstyle{nonumberplain}
\newframedtheorem{defi}{Definition}
\newframedtheorem{theo}{Theorem}
\newframedtheorem{lemma}{Lemma}

@@

\section{Non-Matroid Strategy Spaces}
Finally, we consider in this section non-matroid strategy spaces. Specifically,
we present a construction which illustrates how to obtain a weighted two player
resource buying game with marginally non-increasing cost functions which does
not posses a PNE starting from a non-matroid anti-chain $S$. This implies that
matroids are exactly the structures to consider using marginally non-increasing
cost functions since other structures cannot guarantee the existence of PNEs.
Thus, we prove the following theorem:
\begin{theo}
  For every non-matroid anti-chain $\mathcal{S}$ on a set of resources $E$,
  there exists a weighted two-player resource buying game
  $G = \tupel{\tilde{E},
    (\mathcal{S}_{1}\times \mathcal{S}_{2})\times\mathcal{P},\pi}$
  having marginally non-increasing cost functions, whose strategy spaces
  $\mathcal{S}_{1}$ and $\mathcal{S}_{2}$ are both isomorphic to $\mathcal{S}$,
  so that $G$ does not posses a PNE.
\end{theo}
As said before we start with an anti-chain $\mathcal{S}\subseteq 2^{E}$ which
specifically does \emph{not} satisfy the matroid properties. Hence
$\mathcal{S}$ contains two sets $X, Y$ s.t. there is one element in $X$ for
which we cannot find a single element in $Y$ to obtain an element from
$\mathcal{S}$ again. Intuitively, the dimension of one element in $X$ needs
two elements from $Y$ to be become available. This can be formally described
by the following lemma:
\begin{lemma}
  If $\mathcal{S}\subseteq 2^{E}$ is a non-matroid anti-chain, then there exist
  $X,Y\in\mathcal{S}$ and $\set{a,b,c}\subseteq X\cup Y$ such that each
  $Z\in\mathcal{S}$ with $Z\subseteq(X\cup Y)\setminus\set{a}$ contains both,
  $b$ and $c$.
\end{lemma}
Especially we can guarantee that there are two elements in $\mathcal{S}$ s.t.
one contains $a$ (but not $b$ and $c$) and the other $b$ and $c$ (but not $a$).
In the following we construct a game which does not possess a PNE. The
constructed game is illustrated in Figure \ref{fig:game} for better
understanding.
  \input{tikz/gamediagram}
  \caption{Illustration of constructed game which does not possess a PNE.}
  \label{fig:game}
We consider two isomorphic copies of $\mathcal{S}$:
$\mathcal{S}_{1},\mathcal{S}_{2}$ and by previous lemma there are
$X_{i}, Y_{i}\in\mathcal{S}_{i}$ for $i = 1,2$ as described above. We interleaf
the ground-sets of $\mathcal{S}_{1}$ and $\mathcal{S}_{2}$ by precisely three
elements $x,y,z$ which we identify in both copies differently. Namely, we set
$x = a_{1} = b_{2}$, $y = b_{1} = a_{2}$, and $z = c_{1} = c_{2}$. The set of
resources for $G$ is now the union of both ground-sets w.r.t. the intersection
which is $\set{x,y,z}$. Furthermore we fix the cost functions of all elements
in $\tilde{E}\setminus{X_{1}\cup X_{2}\cup Y_{1}\cup Y_{2}}$ to a high constant
$M$ which ensures that both players only play within $X_{i}, Y_{i}$ (for
$i = 1,2$ respectively). In this \enquote{sub-arena} we set the cost functions
of all elements other than $\set{x,y,z}$ to $0$ regardless of the demand. And
concludingly we set $c_{x}(t) = t$, $c_{y}(t) = 5\frac{1}{2}$, and
$c_{z}(t) = 4$ and an individual demand of the players of $d_{1} = 5$ and
$d_{2} = 4$. Thus, each player either contributes to pay for her/his $a$ or
to $b$ and $c$. Assuming there is a PNE
$\tupel{Z^{\ast} = \tupel{Z_{1}^{\ast}, Z_{2}^{\ast}},
p^{\ast} = \tupel{p_{1}^{\ast}, p_{2}^{\ast}}}$ we can conclude by the choice
of $\set{x,y,z}$ that
\begin{equation*}
  x\notin Z_{1}^{\ast}\Rightarrow \set{y,z}\subseteq Z_{1}^{\ast} \text{ and }
  y\notin Z_{2}^{\ast}\Rightarrow \set{x,z}\subseteq Z_{2}^{\ast}
\end{equation*}
By examining the restricted environment of the cost inducing elements ($x,y,z$)
and the conclusion that one player either only contributes to $x$ or $y$ and
$z$ and the other only to $y$ or $x$ and $z$ one can conclude that neither
$x\in Z_{1}^{\ast}$ nor $x\notin Z_{1}^{\ast}$ which yields a contradiction to
the existence of a PNE and thus concludes the argument on the section-leading
theorem.
